Virtual Memory Assisted Transactional Memory for Dynamic Languages

### 2014-05-28 talk/dls2014/paper/paper.tex
add first (bad) results for JIT in our benchmarks

Here, we will not go into detail about the integration of our STM
system with PyPy's JIT. In fact, we will disable it for all benchmarks
except those in section \ref{sec:real-world-bench}. We would like to
regard it as a simple performance enhancement, but that is not what
happens in reality. First, since the JIT is a tracing
JIT\remi{explain?}  running in multiple threads, it may compile
different things in each run because of the non-deterministic
thread-scheduling of the operating system (OS). Second, it is able to
remove some allocations in some cases. Because compilation is already
non-deterministic, so is this allocation-removal. And third, we did
not have enough time to optimise integration with STM so that the JIT
exposes the overhead of STM more by speeding up all the rest.

Overall, we believe that disabling it on all benchmarks except the
real-world benchmarks in section \ref{sec:real-world-bench} is better
because we can minimise non-determinism. We also do not want to depend
on the capabilities of the JIT in these experiments.

@@

\subsection{Real-World Benchmarks\label{sec:real-world-bench}}

@@

>>>>

Here, we will not go into detail about the integration of our STM
system with PyPy's JIT. In fact, we will disable it for all benchmarks
except those in section \ref{sec:performance-bench}. We would like to
regard it as a simple performance enhancement, but that is not what
happens in reality. First, since the JIT is a tracing
JIT\remi{explain?}  running in multiple threads, it may compile
different things in each run because of the non-deterministic
thread-scheduling of the operating system (OS). Second, it is able to
remove some allocations in some cases. Because compilation is already
non-deterministic, so is this allocation-removal. And third, we did
not have enough time to optimise integration with STM so that the JIT
exposes the overhead of STM more by speeding up all the rest.

Overall, we believe that disabling it on all benchmarks except the
performance benchmarks in section \ref{sec:performance-bench} is better
because we can minimise non-determinism. We also do not want to depend
on the capabilities of the JIT in these experiments.

@@

\subsection{Performance Benchmarks\label{sec:performance-bench}}

\remi{For performance we first look at no-JIT behaviour of STM. Since
we cannot compete well even with CPython, we later show JIT benchmarks
where we see the unstable performance but also that we can still scale.
(with more work we can use our STM system to parallelise jitted code
too)}

@@

% TODO: Jython
\remi{Some benchmarks (figure \ref{fig:performance-jit} with enabled
JIT show that we can be competitive with the other solutions. It also
shows that more work is needed in that area to make performance more
stable.}

\begin{figure}[h]
  \centering
  \includegraphics[width=1\columnwidth]{plots/performance.pdf}
  \caption{Comparing runtime between interpreters with JIT\label{fig:performance-jit}}
\end{figure}
